%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {DevOps Engineer} % Job title
    {BankBazaar.com} % Organization
    {Bangalore, India} % Location
    {May 2015 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Infrastructure orchestration using SaltStack and Python/ bash shell scripting.}
        \item {Maintain production and pre-production environment with high availability.}
        \item {Configure and manage alerting and monitoring systems like Nagios, ELK.}
        \item {Set up complete automated on-demand/ scalable AWS platform for pre-production environment.}
        \item {Troubleshoot/ debug issues related to existing environment.}
        \item {Handle change requests related to infrastructure; maintain SLAs.}
        \item {Setup automatic deployment of Linux containers.}
        \item {Setup Redis Cache Server with automatic failover using Sentinel.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Systems Engineer} % Job title
    {Tata Consultancy Services} % Organization
    {Pune, India} % Location
    {Jun 2012 - Apr 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked in Internal IS team as Linux Team Lead, handling datacenter and storage operations.}
        \item {Managed EMC Storage, like Clariion, Celerra, VNX and VNXe series.}
        \item {Implemented Patch Management server using YUM repository.}
        \item {Migrated existing FTP server to SFTP server.}
        \item {Implemented Kickstart server for un-attended Linux installations.}
        \item {Implemented Syslog server for capturing logs of network devices.}
        \item {Handled audits and performed log analysis, RCAs.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Asst. Systems Engineer} % Job title
    {Tata Consultancy Services} % Organization
    {Pune, India} % Location
    {Aug 2011 - May 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Managed infrastructure servers like, DHCP, DNS, Squid, Syslog, FTP etc.}
        \item {Managed OS deployment using open source tool, FOG.}
        \item {Managed firewalls based on IPTables.}
        \item {Basic Linux administration with user, disk, file, volume management.}
        \item {Handled internal ticketing queue.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
